Open-Set Domain Adaptation through Self-Supervision

### 2022-02-12 paper/main.tex
Implementation details

\subsection{Rotation Recognition}

@@

\subsection{Step I: target known/unknown separation}

@@

@@

\section{Implementation Details}
\label{sec:implementation_details}
\subsection{Model Parameters}
\label{sec:model_parameters}

All models were run using stochastic gradient descent with batch size 32,
a weight decay of 0.0005 and momentum of 0.9.
For single-headed models, 
a base learning rate of 0.001 is used,
while for multi-headed models it is set to 0.003.
This is because only one head of the heads is trained with each samples,
so the process needs to be sped up.
Rotation classifier use a learning rate set to a tenth of the base learning rate.
A step learning rate scheduler is used, reducing it by a factor of 10 after 90\% of epochs.
All models are run for 50 epochs for the first step described in \ref{eq:sample_separation} and for 25 epochs for the second step described in \ref{sec:domain_alignment}.
For model using the center loss a centroid learning rate of 0.5 is used.
All other parameters are configuration-sepcific and are reported in table \ref{tab:params}.
"No Rotation" model is the same as a single-head without center loss model with $\alpha_2 = 0$.

% % %

{\it Extractor E}: The extractor employed is a ResNet-34{\bf[Inserire cit a ResNet]} {\bf è pretrained???} {\bf ma 34 o 18???} for all classifiers.

{\it Classifier $C_1$, $C_2$}: $C_1$ is composed of a 45 dimensional output. 
All unknown samples are mapped as belonging to class 45.
$C_1$ is used as a starting point for $C_2$.
As no unknowns are present on the source dataset (they are removed),
the weight of unknwon samples in the second step is set to {\bf spiegare come è bilanciato} while for all other classes it is set to 1.
A single fully connected layer $512\to 45$ with batch-norm is used.

{\it Classifier $R_1$, $R_2$}: 
$R_1$ and $R_2$ are composed by a $1024\to 256$  and a $256\to 4$ fully connected layers, named {\it Discriminators}.
The 256-dimensional output are the features used by the center loss for inferring class centers.
If multi-head is used, each head is a separate discriminator.
$R_2$ is always a single-head classifier, even if using a multi-head rotation classifier.

>>>>

\subsection{Rotation Recognition}
\label{sec:rotrecognition}

@@

\subsection{Step I: target known/unknown separation}
\label{sec:stepone}

@@

\subsection{Implementation Details}
\label{sec:implementation_details}

As we have already seen in section \ref{sec:method}, the network is composed of a feature extractor $E$, and two heads, $C_{1/2}$ and $R_{1/2}$.
For the feature extraction, we employ a ResNet-18 ({\bf INSERT REF}) pre-trained on ImageNet.
All the experiments are run training with a batch size equals to 32 and using a stochastic gradient descent optimization strategy
with a weight decay of 0.0005 and a momentum of 0.9.
The learning rate is set to 0.001 in the cases where we use a single-head rotation classifier as $R_1$, and 0.003 in the multi-head case.
The reason of this choice lies on the fact that, with a multi-head rotation classifier, we have to train 45 heads instead of a single one,
so the training process needs to be speeded up.
Moreover, we set a learning rate 10 times lower for the feature extractor weights.
We also decrease the learning rate using a step learning rate scheduler, which reduces it by a factor of 10 after 90\% of total epochs.
All models are trained for 50 epochs for the step one and for 25 epochs for the step two.
For models using the center loss a centroid learning rate of 0.001 is used.
The other hyperparameters are analyzed performing an ablation on section {\bf INSERT REF}.

{\it Feature extractor E}: ResNet-18 pre-trained on ImageNet. It is also shared between step 1 and step 2.

{\it Classifier $C_1$}:
It is a simple linear classifier with a 45-dimensional output.

{\it Classifier $C_2$}:
Like $C_1$ but with a 46-dimensional output to consider also the unknown class. Furthermore, it leverages the learning already performed on $C_1$.
It is worth noting that we rebalance the weight of the loss computed on samples belonging to the class unknown in the following way.
After having separated the target into $\mathcal{D}_t^{knw}$ and $\mathcal{D}_t^{unk}$,
we select the weight as $\frac{\mathcal{\bar{D}}_s}{|\mathcal{D}_t^{unk}|}$,
where ${\mathcal{\bar{D}}_s}$ is the average number of samples contained in the source known classes.
This ensures that we correctly balance the unknown class during training in a way which is independent
on the number of identified target unknown samples during the separation.

{\it Classifier $R_1$, $R_2$}: 
they are composed by a linear layer $1024\to 256$, followed by a batch normalization layer and a leaky relu activation.
The last layer is then a linear one for the actual classification $256\to 4$.
The 256-dimensional output are the features used by the center loss for inferring class centroids.
$R_2$ is always a single-head classifier, even if using a multi-head rotation classifier.

@@
